Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-25 paper.qmd
Updated Figure 15 with new projection

## Second projection
projection <- cbind(
    c(-0.4545,-0.5533,-0.1235,0.3984,-0.2065,-0.3586,-0.0088,0.3572,-0.1368),
    c(0.4576,-0.3157,0.4708,0.1410,-0.4479,-0.1685,0.3668,-0.2692,0.1332))

@@

# pbmc_proj_umap_model2 <- projected_df |>
#   ggplot(
#     aes(
#       x = proj1, 
#       y = proj2)) +
#   geom_segment(
#     data = model_df, 
#     aes(
#       x = proj1_from, 
#       y = proj2_from, 
#       xend = proj1_to, 
#       yend = proj2_to), 
#     color = "#33a02c",
#     linewidth = 1) +
#   geom_point(
#     #size = 0.5,
#     alpha = 0.2) +
#   scale_color_manual(values = c("#000000", "#33a02c")) +
#   geom_segment(
#     data=axes, 
#     aes(x=x1, y=y1, xend=x2, yend=y2), 
#     colour="grey70") +
#   geom_text(
#     data=axes,
#     aes(x=x2, y=y2), 
#     label=rownames(axes),
#     colour="grey50",
#     size = 3) +
#   geom_path(
#     data=circle, 
#     aes(x=c1, y=c2), colour="grey70") +
#   coord_fixed() +
#   xlim(c(-0.9, 0.5)) +
#   ylim(c(-0.9, 0.5)) +
#   interior_annotation("a3", cex = 2)

pbmc_proj_umap_model2 <- ggplot() +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.65, 0.65)) +
  ylim(c(-0.65, 0.65)) +
  interior_annotation("a3", cex = 2)

@@

# pbmc_proj_umap_model2_best <- projected_df |>
#   ggplot(
#     aes(
#       x = proj1, 
#       y = proj2)) +
#   geom_segment(
#     data = model_df, 
#     aes(
#       x = proj1_from, 
#       y = proj2_from, 
#       xend = proj1_to, 
#       yend = proj2_to), 
#     color = "#33a02c") +
#   geom_point(
#     #size = 0.5,
#     alpha = 0.2) +
#   scale_color_manual(values = c("#000000", "#33a02c")) +
#   geom_segment(
#     data=axes, 
#     aes(x=x1, y=y1, xend=x2, yend=y2), 
#     colour="grey70") +
#   geom_text(
#     data=axes,
#     aes(x=x2, y=y2), 
#     label=rownames(axes),
#     colour="grey50",
#     size = 3) +
#   geom_path(
#     data=circle, 
#     aes(x=c1, y=c2), colour="grey70") +
#   coord_fixed() +
#   xlim(c(-0.9, 0.5)) +
#   ylim(c(-0.9, 0.5)) +
#   interior_annotation("b3", cex = 2)

pbmc_proj_umap_model2_best <- ggplot() +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.65, 0.65)) +
  ylim(c(-0.65, 0.65)) +
  interior_annotation("b3", cex = 2)

>>>>

## Second projection
projection <- cbind(
    c(0.0734,0.6138,-0.4671,0.2589,0.1189,0.0778,-0.0819,0.0308,-0.5561),
    c(0.6625,0.0034,0.2412,0.3360,0.2463,0.1070,-0.2903,-0.4705,0.1293))

projection_scaled <- projection * 1.25

@@

axes_obj <- gen_axes(
  proj = projection,
  limits = 1.35,
  axis_pos_x = -0.75,
  axis_pos_y = -0.75,
  axis_labels = names(scaled_pbmc_data),
  threshold = 0.12)

pbmc_proj_umap_model2 <- projected_df |>
  ggplot(
    aes(
      x = proj1,
      y = proj2)) +
  geom_segment(
    data = model_df,
    aes(
      x = proj1_from,
      y = proj2_from,
      xend = proj1_to,
      yend = proj2_to),
    color = "#000000") +
  geom_point(
    #size = 0.5,
    alpha = 0.2,
    color = '#a65628') +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2),
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle,
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 0.75)) +
  ylim(c(-1, 0.75)) +
  interior_annotation("a3", cex = 2)

# pbmc_proj_umap_model2 <- ggplot() +
#   geom_segment(
#     data = model_df, 
#     aes(
#       x = proj1_from, 
#       y = proj2_from, 
#       xend = proj1_to, 
#       yend = proj2_to), 
#     color = "#000000") +
#   geom_segment(
#     data=axes, 
#     aes(x=x1, y=y1, xend=x2, yend=y2), 
#     colour="grey70") +
#   geom_text(
#     data=axes,
#     aes(x=x2, y=y2), 
#     label=rownames(axes),
#     colour="grey50",
#     size = 3) +
#   geom_path(
#     data=circle, 
#     aes(x=c1, y=c2), colour="grey70") +
#   coord_fixed() +
#   xlim(c(-0.65, 0.65)) +
#   ylim(c(-0.65, 0.65)) +
#   interior_annotation("a3", cex = 2)

@@

axes_obj <- gen_axes(
  proj = projection,
  limits = 1.35,
  axis_pos_x = -0.75,
  axis_pos_y = -0.75,
  axis_labels = names(scaled_pbmc_data),
  threshold = 0.12)

pbmc_proj_umap_model2_best <- projected_df |>
  ggplot(
    aes(
      x = proj1,
      y = proj2)) +
  geom_segment(
    data = model_df,
    aes(
      x = proj1_from,
      y = proj2_from,
      xend = proj1_to,
      yend = proj2_to),
    color = "#000000") +
  geom_point(
    #size = 0.5,
    alpha = 0.2,
    color = '#999999') +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2),
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle,
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 0.75)) +
  ylim(c(-1, 0.75)) +
  interior_annotation("b3", cex = 2)
